---
title: "Visualize Results"
author: "You!"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

I've used some of my favorite options to compile this document. You can read all about the different options in [Yihui Xie's book](https://bookdown.org/yihui/rmarkdown/).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

First we need to load the data, and `ggplot2` to create the plots.

```{r}
library(ggplot2)
setwd('~/ncf_r_example')
#Unlike `save.img` and `load`, the `saveRDS` and `readRDS` functions save a
#single object to a file, and read back from that file into a variable using
#whatever variable name you want to use.
sim_df <- readRDS('simulation_results_01000.rds')
```

Let's inspect the data frame.

```{r}
knitr::kable(head(sim_df))
```

I think we need to add a column that specifies whether the p-value is < .05, and then summarize the proportion of results that are significant for each N.

```{r}
sim_df$is_sig <- sim_df$pvalue < .05
sim_df_split <- split(x = sim_df, f = sim_df$N)
sim_df_split_summary <- lapply(sim_df_split, function(d){
  N <- d$N[[1]]
  power <- mean(d$is_sig)
  se <- sqrt( power * (1 - power) / dim(d)[[1]] )
  upper <- min(power + qnorm(.975)*se, 1)
  lower <- max(power + qnorm(.025)*se, 0)
  return(data.frame(N = N, power = power, upper = upper, lower = lower))
})
sim_df_summary <- do.call(rbind, sim_df_split_summary)
```

And now we can plot it.

```{r}
ggplot(sim_df_summary, aes(x = N, y = power)) + 
  geom_line(alpha = .5) + 
  geom_point() + 
  geom_linerange(aes(ymin = lower, ymax = upper)) + 
  coord_cartesian(y = c(0, 1))+
  theme_minimal()
```
